\clearpage
\begin{centering}
\textbf{ACKNOWLEDGEMENTS}\\
\vspace{\baselineskip}
\end{centering}

%Insert your dedication text here
Last five years have presented me with amazing opportunities and I have a lot of people to thank for this extraordinary journey. Foremost, my advisor Dr. Martin Maldovan whose passion for science and patience for naive questions made him the perfect mentor for me. I am forever grateful to him for exposing me to a wide-array of ideas; we had some amazing discussions on topics from technology to philosophy, filled with stimulating thoughts and boisterous laughter, which I will always cherish.

I am particularly grateful to Dr. Michael Filler for his feedback on my research and it has been a pleasure to learn from his insights. His podcast, Nanovation, continues to fuel my interest in nanotechnology while making commutes more bearable. I am also grateful to Dr. Zhuomin Zhang, Dr. David Sholl and Dr. Elsa Reichmanis for letting me learn from their vast academic experience and always providing me helpful feedback about my research. 

I would like to acknowledge my experimental collaborators, Dr. Gözde Tütüncüoglu, Dr. Shannon Yee and his research lab, Dr. Sampath Kommandur, Aravindh Rajan and Patrick Creamer. I also thank my group and office-mates Dr. Juan Manuel and Kartik Kothari for amazing discussions we had and ideas that we produced these past years. Georgia Tech has really been a cracking place to work because of all of you! 

I am grateful to the Defense Advanced Research Projects Agency (DARPA), Defense Sciences Office (DSO), and the Army Research Office (ARO) for their financial support of my PhD.

I would like to recognize my mentors at IIT Roorkee, Dr. Shashi and Dr. Surendra Kumar who instilled in me a passion for research. Dr. Shashi was an inspiration for me and will always be dearly missed.

My biggest supporters, my Mom and Dad, thank you for all the things that you have done for me and selflessly supporting me in all my decisions. My brother Dr. Suhail Malhotra for being the best partner in crime. We have always made each other a little better and a little stronger, one day at a time. I am also ever grateful to my sister-in-law Dr. Parminder for her infectious optimism in everything that she does, to Rishi Sidhu for the numerous discussions we continue to share that always make my days brighter, to my uncle Dr. Satpal Ahuja who continues to be a role model to pursue excellence, quietly and honestly, and to all my friends I made in Atlanta, in particular Mayank, Kong and Anshuman, for being a part of special moments that shaped my last five years. 

Finally, the one person who has accompanied me on nearly every step of this journey, Akanksha. She has been my best friend a long time before I decided to come to Georgia Tech. From the decision to come to Atlanta together, to listening to multiple iterations of almost every presentation, she has selflessly been there every step of the way. It was her positive outlook and unending support that propelled me onwards. Thank you for giving meaning to everything that I do.

\clearpage
%\pagenumbering{gobble}  %remove page number on summary page
